Toronto's Most Studious Wards: An Analysis of Annual Toronto Public Library's Circulation and Visits by Wards Pre and Post-COVID

### 2024-01-26 outputs/paper/paper.qmd
final paper upload

# Create Bar Graph
circulation_2022 |>
  ggplot(aes(x = ward_no, y = ward_total)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_x_continuous(breaks = 1:25) +
  scale_y_continuous(limits = c(0, 2400000), breaks = seq(0, 2400000, by = 200000)) +
  labs(x = "Ward Number", y = "Total Annual Circulation")

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-annualcirculation
#| fig-cap: City-Wide Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Year
#| fig-pos: "H"
#| fig-height: 2.5

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-annualvisits
#| fig-cap: City-Wide Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Year
#| fig-pos: "H"
#| fig-height: 2.5

>>>>

# Create Bar Graph
circulation_2022 |>
  ggplot(aes(x = ward_no, y = ward_total)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_x_continuous(breaks = 1:25) +
  scale_y_continuous(limits = c(0, 1600000), breaks = seq(0, 1600000, by = 200000)) +
  labs(x = "Ward Number", y = "Total Annual Circulation")

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-annualcirculation
#| fig-cap: City-Wide Annual Circulation of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Year
#| fig-pos: "H"
#| fig-height: 3.5

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-annualvisits
#| fig-cap: City-Wide Annual Visits of Toronto Public Library Branches (Physical and Fixed Location Branches Only) by Year
#| fig-pos: "H"
#| fig-height: 3.5
